Look, we can do something

### 2024-10-21 paper.tex
Summary

For comparison, we do the same sorting across groups for roundness
parameter. The results are on
\cref{fig:convexity-groups-roundness}. Well-clusterized pores have the biggest
roundness for convexity $C > 0.8$. For lower convexity, however, even pores with
the biggest roundness in the group are also underclusterized while
\highlight{awesomeness} parameter is capable of separating well-clusterized and
underclusterized pores.
\begin{figure*}
  \centering
  \subfigure[$0.55 \le C < 0.65$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.60.png}}
  \hfill
  \subfigure[$0.65 \le C < 0.75$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.70.png}}
  \vskip\baselineskip
  \subfigure[$0.75 \le C < 0.85$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.80.png}}
  \hfill
  \subfigure[$0.85 \le C < 0.95$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.90.png}}
  \caption[]{Pores divided into groups by their convexity. Upper row of each
    subfigure: pores with minimal \highlight{awesomeness} in the group, lower
    row: pores with maximal \highlight{awesomeness} in the group.}
  \label{fig:convexity-groups-score}
\end{figure*}

@@

>>>>

For comparison, we do the same sorting across groups for roundness
parameter. The results are on
\cref{fig:convexity-groups-roundness}. Well-clusterized pores have the biggest
roundness for convexity $C > 0.8$. For lower convexity, however, even pores with
the biggest roundness in the group are also underclusterized while
\highlight{awesomeness} parameter is capable of separating well-clusterized and
underclusterized pores.
\begin{figure*}
  \centering
  \subfigure[$0.55 \le C < 0.65$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.60.png}
    \label{fig:small-gap}}
  \hfill
  \subfigure[$0.65 \le C < 0.75$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.70.png}}
  \vskip\baselineskip
  \subfigure[$0.75 \le C < 0.85$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.80.png}}
  \hfill
  \subfigure[$0.85 \le C < 0.95$]{
    \includegraphics[width=0.4\linewidth]{images/groups-score-0.90.png}
    \label{fig:small-blob}}
  \caption[]{Pores divided into groups by their convexity. Upper row of each
    subfigure: pores with minimal \highlight{awesomeness} in the group, lower
    row: pores with maximal \highlight{awesomeness} in the group.}
  \label{fig:convexity-groups-score}
\end{figure*}

@@

\section{Summary}
In this paper we have developed a new parameter for assession of pore
clusterization quality which can be used as a replacement for roundness
parameter. Benefits of this parameter include:
\begin{itemize}
\item Lower absoulute value of correlation with other common parameters, such as
  convexity, elongation and roundness.
\item Ease of computation.
\item Ability to precisely separate well-clusterized pores and underclusterized
  pores in a high convexity range, even if roundness fails to do so.
\item Rotation and resize invariance.
\end{itemize}

Flaws of this parameter include:
\begin{itemize}
\item C-shaped pores with a small gap, like the pore on the left-top of
  \cref{fig:small-gap} always have small \highlight{awesomeness}, even if they
  are otherwise clusterized correctly.
\item Small changes to an image of a pore, when cleverly done, can make drastic
  changes in \highlight{awesomeness}.
\end{itemize}

The first flaw can be dealt with by replacing the Euclidean distance in
\cref{eq:intro} with the length of the shortest path between points which does
not cross the pore's boundary. This, however, can increase computational time
significantly.

The second flaw means that a pore with a very small attachment (compared to the
pore's total surface) connected with a thin throat to the pore's main body has
low \highlight{awesomeness}, like the third pore on \cref{fig:small-blob}, a row
on the top. Normally, small attachments like this do not contribute to any
physical process in any way, so they can simply be ignored and, therefore, their
impact on \highlight{awesomeness} may be not justified.
